A tale of two cities: A GIS based data synthesis approach to understanding semantic decompositions of Twitter user locations

### 2017-01-18 semantic_decomposition_of_twitter_user_locations/paper.tex
edits

\begin{document}
% \title{A data synthesis approach for semantic decompositions of Twitter user locations: A case study of geo-located Twitter data in Chicago}
\title{A tale of two cities: A GIS based data synthesis approach to understanding semantic decompositions of Twitter user locations}
% \author~\thanks{yinjunjun@gmail.com]{Junjun Yin}
\author[1,~\thanks{Corresponding author: jyin@psu.edu}]{Junjun Yin}
\affil[1]{Population Research Institute}
\affil[ ]{The Pennsylvania State University, State College, 16801, PA, USA}
\renewcommand\Authands{ and }
\maketitle

\section*{Abstract}
Today's pervasive Location Based Social Media provide abundant user-generated geographic information
In this paper, we present a geographical information system (GIS) based data synthesis approche to understanding semantic decompositions of Twitter user locations.
Specifically, we implemented a
This approach 
We analyzed the

@@

\section{Related Work}

\section{Methods and Materials}

>>>>

\begin{document}
% \title{A data synthesis approach for semantic decompositions of Twitter user locations: A case study of geo-located Twitter data in Chicago}
\title{A tale of two cities: A GIS based data synthesis approach to understanding semantic decompositions of Twitter user locations}
\author[1~\thanks{Corresponding author: jyin@psu.edu}]{Junjun Yin}
\affil[ ]{Social Science Research Institute}
\affil[ ]{The Pennsylvania State University, State College, 16801, PA, USA}
\renewcommand\Authands{ and }
\maketitle

\section*{Abstract}
Human mobility is as complex human behavior, by its nature difficulty to study, confounded by human variability.

With the advancement positioning technology, the

Today's pervasive Location Based Social Media provide abundant user-generated geographic information
In this paper, we present a geographical information system (GIS) based data synthesis approach to understanding semantic decompositions of Twitter user locations.
Specifically, we implemented a
This approach 
We analyzed the

@@

\section{Related Work}
yy~\cite{yin2017depicting}

\section{Data and Methods}
